---
title: "Basic networ visualization"
output:
  html_notebook: default
  html_document: default
---

## Functions used for this visualization

### Function to clean data

```{r}

removeSwappedDupKeyValueDf <- function(x){
  foo <- igraph::graph_from_data_frame(x,directed=FALSE)
  foo <- igraph::simplify(foo,edge.attr.comb = list("first"))
  foo <- igraph::as_data_frame(foo,what='edges')
  return(foo)
}
```


### Creating weighter adjacency matrix 

```{r}
get.weighted.adjacency <- function(Net){
  
 Nam <- names(V(Net))
 EL <- get.edgelist(Net)
 W <- E(Net)$weight
 A <- matrix(0, nrow = length(Nam), ncol = length(Nam))
  
 for (i in 1:length(EL[,1])){
   
   In1 <- grep(EL[i,1],Nam)
   In2 <- grep(EL[i,2],Nam)
   
   A[In1,In2] = W[i]
   A[In2,In1] = W[i]
   
 }
  
 return(A)
  
}

```



### Plotting a graph given labels for nodes (and node sizes)


```{r}
GenGraphViz <- function(x, pattern, Types,
                        sizeMin = 3, sizeMax = 10){
  
  #identifying subset of data to use
  print('Obtaining sub-graph based on brain region')
  In1 <- grep(pattern,Dat$from)
  In2 <- grep(pattern,Dat$to)
  In_int <- intersect(In1,In2)
  Dat <- Dat[In_int,]
  
  #annotating nodes by algorithm type
  print('Annotating nodes by algorithm type')
  ModNames <- c()
  ModType <- c()
  TypeName <- c()
  
  l <- length(Types)
  
  for (i in 1:l){
    temp <- union(grep(Types[i],Dat$from, value= TRUE),
                  grep(Types[i],Dat$to, value= TRUE))
    ModNames <- c(ModNames,temp)
    ModType <- c(ModType,rep(i,length(temp)))
    cat('No. of modules in',Types[i],length(temp),'\n')
    TypeName <- c(TypeName, rep(Types[i],length(temp)))
  }
  
  #creating visualization 
  print('Creating visualization')
  df <- data.frame(Name = ModNames, ModType = ModType, 
                   TypeName = TypeName)
  library('igraph')
  df2 <- data.frame(from = Dat$from, 
                    to = Dat$to,
                    weight =  (1/(1e-50 + c(Dat$fisherOR)^1)))
  net <- graph.data.frame(df2, vertices=df, directed=F) 
  
  #coloring nodes on the basis of module type 
  cmap <- rainbow(l, alpha=1) 
  V(net)$color <- cmap[V(net)$ModType]
  deg <- 1/(1e-50 + strength(net))
  V(net)$size <- sizeMin + deg/max(deg)*sizeMax
  #l <- layout_with_fr(net, niter = 5000, grid = 'nogrid')
  l <- layout_with_graphopt(net, niter= 500, charge = 0.01, mass = .0001,
                             spring.constant = 10)
  
  E(net)$width <- 1*(E(net)$weight - min(E(net)$weight))/max(E(net)$weight)
  #E(net)$width[E(net)$width <= median(E(net)$weight)] <- 0
  m <- median(E(net)$weight)
  net <- delete_edges(net, E(net)[weight<m])

  #l <- layout_with_kk(net)
  A <- get.weighted.adjacency(net)
  #library(tsne)
  #l <- tsne(A)
  plot(net, vertex.label = NA, edge.width = E(net)$width,  
       layout=l)
  legend(x=-1.5, y=-1.1,Types,pch=21,col="#777777", pt.bg=cmap,
         pt.cex=2, cex=.8, bty="n", ncol=1)
  
  #returning igraph object and layout
  RetDat <- list()
  RetDat$net <- net 
  RetDat$l <- l 
  return(RetDat)
  
  
}
```

### Getting list of all genes in a set of modules 

```{r}

GetGenesModules <- function(brainRegion, ModuleNames){
  
  ConsensusGeneMods <- synapseClient::synTableQuery(paste0("SELECT * FROM syn10337531 
                                                           where brainRegion = 
                                                           '",brainRegion,"'"))@values
  
  OtherGeneMods <- synapseClient::synTableQuery(paste0("SELECT * FROM syn10309369 
                                                         where brainRegion = 
                                                         '",brainRegion,"'"))@values
  
  In <- which(ConsensusGeneMods$ModuleNameFull %in% ModuleNames)
  ConsensusGeneMods <- ConsensusGeneMods[In,]
  
  In <- which(ConsensusGeneMods$ModuleNameFull %in% ModuleNames)
  OtherGeneMods <- OtherGeneMods[In,]  
  
  AllGeneMods <- rbind(ConsensusGeneMods, OtherGeneMods)

  
  return(AllGeneMods)
}


```




#Main program

### Log into Synapse

```{r}
#synapseClient::synapseLogin()
```



### Downloading network modules and pairwise scores

```{r}
Dat <- synapseClient::synTableQuery("SELECT * FROM syn10339153 where ModuleNameFull like '%TCX' and category like '%TCX'")@values
Dat <- removeSwappedDupKeyValueDf(Dat)
Dat <- dplyr::mutate(Dat,adj=p.adjust(fisherPval,method='fdr'))
Dat <- dplyr::filter(Dat,adj<=0.05)
#Drop rows with infinite fisherOR
In <- which(Dat$fisherOR==Inf)
Dat <- Dat[-In, ]
#m <- median(Dat$fisherOR) #keeping only top half of significant interactions
#In <- which(Dat$fisherOR<m)
#Dat <- Dat[-In, ]
```

### Keeping only modules that are significant for AD 

```{r}

Dat2 <- synapseClient::synTableQuery("SELECT * FROM syn10516371 where ModuleBrainRegion = 'TCX'")@values

In <- intersect(which(Dat$from %in% Dat2$ModuleNameFull), 
                which(Dat$to %in% Dat2$ModuleNameFull))
Dat <- Dat[In,]

```



### Generating visualization colored by network type

```{r}
pattern <- "TCX"
Types <- c('consensus','megena','metanetwork','rWGCNA','speakEasy','wina')
RetGraph <- GenGraphViz(Dat,pattern, Types)
Net <- RetGraph$net 
lt <- RetGraph$l 
```
###Printing the number of enriched modules 

```{r}

EnrichedModuleNames <- names(V(Net))
print(EnrichedModuleNames)

```

###Get the list of all genes in the enriched modules 

```{r}

AllGeneNames <- GetGenesModules(pattern, EnrichedModuleNames)
head(AllGeneNames)

```

### Generate heatmap of correlation 

```{r}
Temp <- synGet('syn10624996')
ExpDat <- readRDS(Temp@filePath)
ExpDat <- ExpDat$mayoTCX[unique(AllGeneNames$GeneID)]
SubSampleDepth <- 500
RandIn <- sample.int(length(names(ExpDat)), SubSampleDepth)
ExpDat <- ExpDat[,RandIn]
CorMat <- cor(ExpDat)

pheatmap::pheatmap(CorMat)


```


